{\bf Design Goals.} Our measurement results motivate 
 the design and implementation of a relay-based avoidance system,
\system{}, with the following design goals.
\label{goals}
\begin{itemize}
\item {\bf Country Avoidance.}  The primary goal of \system{} is to
avoid a given country when accessing web content.  \system{} should
provide clients a way to route around a specified country when
accessing a domain.  This calls for the role of measurement in the
system design and systematizing the measurement methods discussed
earlier in the paper.

\item {\bf Usability.} \system{} should require as little effort as
possible from clients.  Clients should not have to download
or install software, collect any measurements, or understand how the
system works.  This requires a way for clients to automatically and
seamlessly multiplex between relays (proxies) based on different
destinations.  \system{} uses a Proxy Autoconfiguration (PAC) file to support this
function.  PAC files are supported on many types of devices, including mobile 
devices (smartphones, tablets, etc.).  Additionally, this is a mechanism that 
is already being used in systems and tools.  Many Internet users that 
use a VPN have {\it already} used a PAC file; when a user establishes a VPN connection, his 
device's proxy settings are modified to point to a PAC file.  

\item {\bf Scalability.}  This country avoidance system should be able to scale to 
many users.  Therefore, \system{} should be able to handle the addition
 of relays, as well as be cost-effective in terms of resources required. This requires 
clever measurement vantage points, such that each vantage point is representative of 
more than one client.  The PAC file allows \system{} to 
grow with the number of clients and also supports incremental deployment.

\item {\bf Non-goals.}  There are some challenges that \system{} does not
attempt to  solve; in particular, it does not provide anonymity; it routes
around  countries,
but it does not attempt to keep users anonymous in the event that traffic can
be observed.   \system{} also does not address domestic interference or surveillance. For
example, a client in the U.S. cannot use \system{} to avoid network interference 
by the United States. 
\end{itemize}
