\section{Discussion}
\label{discussion}

\paragraph{Avoiding multiple countries.} 
We have studied only the extent to which Internet paths can be
engineered to avoid a {single} country.  Yet, avoiding a single country
may force an Internet path into {\em other} unfavorable
jurisdictions. This possibility suggests that we should also be
exploring the feasibility of avoiding multiple surveillance states (\eg,
the ``Five Eyes'') or perhaps even entire regions. It is already clear
that avoiding certain combinations of countries is not possible, at
least given the current set of relays; for
example, to avoid the US, Kenyan clients rely on the relay located in
Ireland, so avoiding both countries is often impossible.

\paragraph{The evolution of routing detours and avoidance over time.}
Our study is based on a snapshot of Internet paths. Over time, paths
change, hosting locations change, IXPs are built, submarine cables are
laid, and surveillance states change.  Furture work can and should
involve exploring how these paths evolve over time, and analyzing the
relative effectiveness of different strategies for controlling traffic flows.

\paragraph{Isolating DNS disversity vs. path diversity.}
In our experiments, the overlay network relays perform DNS lookups from
geographically diverse locations, which provides some level of DNS
diversity in addition to the path diversity that the relays inherently
provide. This approach somewhat conflates the benefits of DNS diversity
with the benefits of path diversity and in practice may increase
clients' vulnerability to surveillance, since each relay is performing
DNS lookups on each client's behalf. We plan to conduct additional
experiments where the client relies on its local DNS resolver to map
domains to IP addresses, as opposed to relying on the relays for both
DNS resolution and routing diversity.
