\section{Related Work}
\label{related}

{\bf Internation Routing Analysis.}  Recently, Shah and Papadopoulos measured international BGP detours (paths that originate in one country, cross international borders, and then return to the original country)~\cite{shah2015characterizing}.  Using BGP RIB files, they found 2 million detours in each month of their study, and they then characterized the detours based on detour dynamics and persistence.  Our work differs in a few ways; we rely on the data-plane to measure international detours (which we call tromboning paths), and we characterize detours based on which countries they transit.  Obar and Clement analyzed traceroutes that started and ended in Canada, but ``boomeranged'' through the United States (``boomerang'' is another term for tromboning), and argued that this is a violation of Canadian network sovereignty~\cite{obar2012internet}.  Most closely related to our work, Karlin, Forest, and Rexford developed a framework for country-level routing analysis to study how much influence each country has over interdomain routing~\cite{karlin2009nation}.  This work measures the centrality of a country to routing and uses AS-path inference to measure and quantify country centrality, whereas our work uses active measurements and measures avoidability of a given country.

{\bf Circumvention Systems.}  There has been research into circumvention systems, particularly for censorship circumvention, that is related this work, but not sufficient for surveillance circumvention.  Tor is an anonymity system that uses 3 relays and layered encryption that allows users to communication anonymously~\cite{dingledine2004tor}.  Anonymity has different requirements than surveillance circumvention; for anonymity, it does not matter which country the traffic is routed through, but it does for surveillance.  In the case that a client can pick the locations of the 3 relays in a Tor circuit, it is still not guaranteed that the paths between the relays do not transit an unfavorable country.  Another existing system is VPNGate, which is a public VPN relay system aimed at circumventing national firewalls~\cite{nobori2014vpn}.  Unfortunately, VPNGate does not allow a client to choose any VPN available, which makes surveillance avoidance harder and possible impossible.

{\bf Mapping Local Internet.}  In 2011, Roberts et. al., described a method for mapping national networks of ASes, identifying ASes that act as points of control in the national network, and measuring the complexity of the national network~\cite{roberts2011mapping}.  There have also been a number of studies that measured and classified the network within a country.  Wahlisch et. al. measured and classified the ASes on the German Internet~\cite{wahlisch2010framework, wahlisch2012exposing}, Zhou, Zhang, and Zhang measured the complete Chinese Internet topology at the AS level~\cite{zhou2007chinese}, and Bischof, Rula, and Bustamante characterized the current state of Cuba's connectivity with the rest of the world~\cite{bischof2015and}.  Interconnectivity has also been studied at the continent level; Gupta et. al. first looked at ISP interconnectivity within Africa~\cite{gupta2014peering}, and it was studied later by Fanou, Francois, and Aben~\cite{fanou2015diversity}.
