\section{Introduction}
\label{intro}

When Internet traffic enters a country, it becomes subject to that
country's laws.  As a result, users have more need than ever to
determine---and control---which countries their traffic is traversing.
For example, an increasing number of countries have passed laws that
facilitate mass surveillance of their
networks~\cite{france_surveillance, netherlands_surveillance,
  kazak_surveillance, uk_bill}. Government and citizens alike may want
to divert their Internet traffic from countries that perform
surveillance (notably, the United States~\cite{russia_secure_internet,
  routing_errors, dte}).

Many countries are taking impressive measures to reduce the likelihood
that Internet traffic transits the United States~\cite{brazil_history,
  brazil_break_from_US, brazil_conference, brazil_conference2,
  brazil_human_rights}.  For example, Brazil is building a 3,500-mile
long fiber-optic cable from Fortaleza to Portugal (with no use of
American vendors); pressing companies such as Google, Facebook, and
Twitter (among others) to store data locally; and mandating the
deployment of a state-developed email system (Expresso) throughout the
federal government (instead of what was originally used, Microsoft
Outlook)~\cite{brazil_cable, brazil_us_companies}.  Brazil is also
building Internet Exchange Points (IXPs)~\cite{brazil_IXP1}, now has the
largest national ecosystem of public IXPs in the
world~\cite{brazil_ixp_ecosystem}, and the number of internationally
connected Autonomous Systems (ASes) continues to
grow~\cite{brazil_international_ases}. And, Brazil is not alone: IXPs
are proliferating in eastern Europe, Africa, and other regions, in part
out of a desire to ``keep local traffic local''. Building IXPs alone, of
course, cannot guarantee that Internet traffic for some service does not
enter or transit a particular country: Internet protocols have no notion
of national borders, and interdomain paths depend in large part on
existing interconnection business relationships (or lack thereof).

Although end-to-end encryption stymies surveillance by concealing URLs
and content, it does not protect all sensitive information from prying
eyes. First, many websites do not fully support encrypted browsing by
default; a recent study showed that more than 85\% of the most popular
health, news, and shopping sites do not encrypt by
default~\cite{what_isps_can_see}; migrating a website to HTTPS is
challenging, and doing so requires all third-party domains on the site
(including advertisers) to use HTTPS.  Second, even encrypted traffic
may still reveal a lot about user behavior: the presence of any
communication at all may be revealing, and website fingerprinting can
reveal information about content merely based on the size, content, and
location of third-party resources that a client loads~\cite{Johnson2013a}. DNS traffic is
also revealing and is essentially never
encrypted~\cite{what_isps_can_see}.  Third, ISPs often terminate TLS
connections, conducting man-in-the-middle attacks on encrypted traffic
for network management purposes~\cite{mitm_isp}.  And, of course,
encryption offers no solution to interference, degradation, or blocking
of traffic that a country might perform on traffic that crosses its
borders.  Circumventing surveillance and interference thus requires not
only encryption, but also mechanisms for controlling where traffic goes
in the first place.

In this paper, we study two questions: (1)~Which countries do {\em
  default} Internet routing paths traverse?; (2)~What methods can help
help governments and citizens
better control transnational Internet paths?  In contrast to previous
work~\cite{karlin2009nation}, which simulates Internet paths, we
\textit{actively measure} and analyze the paths originating in five
different countries: Brazil, Netherlands, Kenya, India, and the United
States.  We study these countries for different reasons, including their
efforts made to avoid certain countries, efforts in building out IXPs,
and their low cost of hosting domains.  Our work studies the
router-level forwarding path, which differs from all other work in this
area, which has analyzed Border Gateway Protocol
(BGP) routes~\cite{karlin2009nation,shah2015characterizing}.  Although
BGP routing can offer some information about paths, it does not
necessarily reflect the path that traffic actually takes, and it only
provides AS-level granularity, which is often too coarse to make strong
statements about which countries that traffic is traversing.  In
contrast, we measure routes from RIPE Atlas probes in five
countries to the Alexa Top 100 domains for each country; we directly
measure the paths not only to the websites corresponding to
themselves, but also to the sites hosting any third-party content on
each of these sites.

Determining which countries a client's traffic traverses is challenging, for
several reasons.  First, performing direct measurements is more costly
than passive analysis of BGP routing tables; RIPE Atlas, in particular,
limits the rate at which one can perform measurements.  As a result, we
had to be strategic about the origins and destinations that we selected
for our study. As we explain in Section~\ref{surv}, we study five
geographically diverse countries, 
focusing on countries in each region that are
making active attempts to thwart transnational Internet paths.  Second,
IP geolocation---the process of determining the geographic location of an
IP address---is notoriously challenging, particularly for IP addresses
that represent Internet infrastructure, rather than end-hosts. We cope
with this inaccuracy by making conservative estimates of the extent of
routing detours, and by recognizing that our goal is not to pinpoint a
precise location for an IP address as much as to achieve accurate
reports of {\em significant} off-path detours to certain countries or
regions. (Section~\ref{datasets} explains our method in more detail; we
also explicitly highlight ambiguities in our results.) Finally, the
asymmetry of Internet paths can also make it difficult to analyze the
countries that traffic traverses on the reverse path from server to
client; our study finds that country-level paths are often asymmetric,
and, as such, our findings represent a lower bound on transnational
routing detours.

We first {\em characterize the current state of transnational Internet
routing detours} (Section~\ref{datasets}).  We explore hosting diversity
and find that only about half of the Alexa Top 100 domains in the five
countries studied are hosted in more than one country; in many cases,
that country is one that clients may want to avoid. Second, even if
hosting diversity can be improved, routing can still force traffic
through a small collection of countries (often surveillance
states). Despite strong efforts made by some countries to ensure their
traffic does not transit certain countries~\cite{brazil_history,
  brazil_break_from_US, brazil_conference, brazil_conference2,
  brazil_human_rights}, their traffic still does so.  For example,over 50\% of the
top domains in Brazil and India are hosted in the United States, and
over 50\% of the paths from the Netherlands to the top domains transit
the United States.  About half of Kenyan paths to the top domains
traverse the United States and Great Britain (but the same half does not
traverse both countries).  Much of this phenomenon is due to
``tromboning'', whereby an Internet path starts and ends in a country,
yet transits an intermediate country; for example, about 13\% of the
paths that we explored from Brazil tromboned through the United States.
%Infrastructure building alone is not enough. ISPs in respective regions
%need better encouragements to interconnect with one another to ensure
%that local traffic stays local.

Next, we {\em explore the
potential effectiveness of building an network of overlay relays to help
clients certain countries}  (Section~\ref{avoid_results}) .  We find that this technique can be effective
for clients in certain countries, yet the effectiveness depends on the
country.  For example, Brazilian clients could completely avoid Spain,
Italy, France, Great Britain, Argentina, and Ireland (among others),
even though the default paths to many popular Brazilian sites traverse
these countries. We also find that some of the most prominent
surveillance states are also some of the least avoidable countries.  For
example, many countries depend on ISPs in the United States, a known
surveillance state, for connectivity to popular sites and content.
Additionally, overlay network relays can keep local traffic local: by
using relays in the client's country, fewer paths trombone out of the
client's country.

Finally, we {\em design, implement and deploy \system{}, a system that allows
a client to access web content without traversing a specified country}
(Section~\ref{system_design}).  \system{} uses a series of overlay
network relays to automatically route a client's traffic around a
specified country.  We design and implement \system{} for country
avoidance, usability, and scalability.  Our evaluation shows that 
\system{} is effective for avoiding many different countries and
introduces minimal performance overhead.
